Autoignition of Methyl Valerate at Low to Intermediate Temperatures and Elevated Pressures in a Rapid Compression Machine

### 2017-06-27 methyl-valerate.tex
Update simulation-comparison

\Cref{fig:simulation-comparison} compares experimentally measured overall
ignition delays with ignition delays computed with the detailed model of
\cite{Dievart2013} for the $\phi=1.0$ experiments. Results for the other
equivalence ratios are similar to these results, so are not shown here. It is
important to note that the model of \cite{Dievart2013} was not validated for
MV ignition delays, only for extinction strain rates. At \SI{15}{\bar}, the
model tends to under-predict the ignition delay and predicts an NTC region that
is not present in the experiments. At \SI{30}{\bar}, the model predicts the
low-temperature ignition delays well, but does not predict the NTC region found
experimentally.

>>>>

\Cref{fig:simulation-comparison} compares experimentally measured overall ignition delays with
ignition delays computed with the detailed model of \citet{Dievart2013} for the \(\phi=1.0\)
experiments. Results for the other equivalence ratios are similar to these results, so are not shown
here. It is important to note that the model of \citet{Dievart2013} was not validated for MV
ignition delays, only for extinction strain rates. At \SI{15}{\bar}, the model tends to
under-predict the ignition delay and predicts an NTC region that is not present in the experiments.
At \SI{30}{\bar}, the model predicts the low-temperature ignition delays well, but does not predict
the NTC region found experimentally.
